A Switching Planner for Combined Task and Observation Planning

### 2010-11-30 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
reading over what we wrote for switching

For the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session. If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
executed, then the current sequential plan is executed until further
sensing is scheduled, or to completion. Lastly, we note that in our
project the rewards, i.e., functions
$\$,\hat\$:2^\propositions\to\Re$, for the POMDP posed to the
contingent session are sourced from a motivational component of our
robotic architecture. For this paper, we set $\$(x)$ to be a positive
constant, and have $\hat\$(x)= - \$(x)(1 - p) / p$ where $p$ is the
probability that $x$ is true.

@@

The starting belief-state for the abstract process is given in terms
of a {\em relaxed} $(\pp{:init})$ declaration. We first construct a
tree which only includes terms from the {\em relaxed} visitation
characterised by the active {\em assumptive} actions in the current
sequential plan. Figure \ref{fig:abstraction} shows the belief state
of a more detailed version of our previous example. The diamonds
represent probabilistic terms of the state description while circles
represent conjunctive or atomic terms.

@@

  \subfloat[The initial belief state with the assumptions made by the continual
    planner.]{

@@

  \subfloat[Re-add relevant facts until the belief space limit is reached.]{

@@

In the first step, we remove all facts that are not part of an
assumption (Fig. \ref{fig:abstraction-b}). At this point, the session
would proceed in an abstraction of the environment where that does not
contain $\pp{place2}$, the $\pp{cup}$ or a $\pp{kitchen}$.

In a second step, we iteratively refine the relaxed declaration by
adding terms from the original statement of $(\pp{:init})$ while the
number of abstract states in $\bstate_0$ that occur with non-zero probability
according to that refined declaration remains of a practicable
size. In detail, for each excluded atomic term, we compute the {\em
  entropy} of the active assumptions, {\em conditional} on the
corresponding proposition.  Loosely speaking, the lower the {\em
  conditional entropy} of an atom is, the more information about the
assumptions can the contingent planner expect to derive from it. Thus,
propositions that in the first place were excluded are iteratively
added to the problem posed to the conditional session in increasing
order according to that measure (Fig. \ref{fig:abstraction-c}).

>>>>

For the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session. If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
executed, then the current sequential plan is executed until further
sensing is scheduled, or to completion. Lastly, we note that in our
project the rewards, i.e., functions
$\$,\hat\$:2^\propositions\to\Re$, for the POMDP posed to the
contingent session are sourced from a motivational component of our
robotic architecture. In this paper, for $\assumptiveDT{i}$ actions
we set $\$(x)$ to be a positive constant, and have $\hat\$(x)= -
\$(x)(1 - p) / p$ where $p$ is the probability that $x$ is true. For
$\actions.\poss(\switchAction)$ actions we have $\hat\$(x)= -
\$(x)p/(1-p)$.\footnote{These values were chosen to encourage sensing.}

@@

The starting belief-state for the abstract process is given in terms
of a {\em relaxed} $(\pp{:init})$ declaration. We first construct a
tree which only includes terms from the {\em relaxed} visitation
characterised by the active {\em assumptive} actions in the current
sequential plan. Figure \ref{fig:abstraction} shows the belief-state
of a more detailed version of our previous example. The diamonds
represent probabilistic terms of the state description while circles
represent conjunctive or atomic terms.

@@

  \subfloat[The initial belief-state with the assumptions made by the continual
    planner in bold.]{

@@

  \subfloat[Refinement, by adding relevant facts until the $\bstate_0$ size limit is reached.]{

@@

In the first step, we remove all facts that are not part of an
assumption (Fig. \ref{fig:abstraction-b}). At this point, the session
would proceed in an abstraction of the environment that does not
contain $\pp{place1}$, the $\pp{cup}$ or a $\pp{kitchen}$. 
%%
In a second step, we iteratively refine the relaxed declaration by
adding terms from the original statement of $(\pp{:init})$ while the
number of abstract states in $\bstate_0$ that occur with non-zero
probability according to that refined declaration remains of a
practicable size. In detail, for each excluded atomic term, we compute
the {\em entropy} of the active assumptions, {\em conditional} on the
corresponding proposition.  Loosely speaking, the lower the {\em
  conditional entropy} of an atom, the more information about the
assumptions the contingent planner expect to derive from it. Thus,
propositions that in the first place were excluded are iteratively
added to the problem posed to the conditional session in increasing
order according to that measure (Fig. \ref{fig:abstraction-c}).
